Large Language Models in Reinforcement Learning - A Comparison of Methods

### 2023-10-17 doc/paper.tex
Fix spelling error
Signed-off-by: Jonatan Hanssen <jonatan.hanssen@outlook.com>
add ethics statement

A standard PPO algorithm with no LLM integration, as a baseline. In this case, use StableBaselines' implementation with the following hyperparameters: HYPERPARAMETERS HERE.

@@

In this case, the LLM is integrated as part of the PPO algorithm, directly influencing the actions taken. This is done as follows: First, the observation is captioned and given as input to the LLM, which is prompted to suggest an action. Then, all actions that the agent could take given the current state are described in natural language. All possible actions are compared with the suggested action, and given a value which denotes their semantic similarity. These values are joined with the probability values that the normal PPO algorithm outputs and normalized, and a new probability distribution is created, where semantically similar actions are weighted higher than others.

@@

>>>>

A standard PPO algorithm with no LLM integration, as a baseline. In this case, we use StableBaselines' implementation with the following hyperparameters: HYPERPARAMETERS HERE.

@@

In this case, the LLM is integrated as part of the PPO algorithm, directly influencing the actions taken. This is done as follows: First, the observation is captioned and given as input to the LLM, which is prompted to suggest an action. Then, all actions that the agent could take given the current state are described in natural language. All possible actions are compared with the suggested action, and given a value which denotes their semantic similarity. These values are joined with the probability values that the normal PPO algorithm outputs and normalized, and a new probability distribution is created, where semantically similar actions are weighted higher than others. We call this the Actor-Advisor-Critic Model.

@@

\section*{Ethics Statement}

In accordance with the NeurIPS Code of Ethics ***ADD REFERENCE HERE***, we outline ethical considerations related to this project, covering potential consequences from the research, and how potential risks may be mitigated. Considering that our research does not involve participants nor sensitive data, concerns related to how such factors are treated will not be discussed.

\subsection{Societal Impact and Potential Harmful Consequences}

Due to how this research project revolves around the integration of LLMs in the RL domain, many of the same concerns that exist in the domain of LLMs themselves are extended to the RL domain. A major concern is that of safety; if the RL agent is to act in an environment where failure to act optimally could be critical, it is paramount that the agent does not enter bad states due to the existing randomness in the RL framework. The LLM in itself predicts stochastically, and thus may add even more noise to the framework. In the worst case, it could amplify probabilities of the agent choosing dangerous actions due to this added noise.

Another topic of concern is that of bias and fairness; the premise for why an LLM might help an RL agent in a large environment is because of its inherent human knowledge, stemming from the human-written texts it has been trained upon. However, human-written texts are an obvious potential source to biased opinions, and the LLM may have learned such biased and/or unfair opinions. Then, in an example where the RL agent is deployed in environments where an ethical choice has to be made, this choice could be influenced by whatever bias may be present in what the LLM suggests to the agent.

\subsection{Impact Mitigation Measures}

As is exemplified above, major ethical concerns regarding the use of our proposed algorithms arise when they are deployed for critical tasks, for instance tasks in real-life dangerous environments, or environments where ethical considerations have to be addressed. Therefore, an agent trained on our proposed RL framework for such critical tasks should be carefully tested before deployment to see if, and how often, critical deviations occur.

In the further development of this and similar algorithms, we also consider it essential to put effort into trying to understand the causality behind certain actions being taken, as is being done in the field of explainable artificial intelligence (XAI). When involving one major ML framework like that of LLMs into RL, we would ideally want to see exactly where and how much the LLM contributes to the RL networks being updated. This would, in turn, help in the work to mitigate whatever biases and variance that may be added to the RL framework from integrating the LLM.
